
\subsubsection{Alpha Sensor:}
Coresense firmware communicates with alpha sensor through SPI.
The raw SPI readings from the board are packetized as the raw value as they are collected, and the reading will be sorted out in database.
In this document, concise Alpha sensor information is provided. For more information, refer to \textbf{`Firmware commands version 18.xls' and `OPC-N2 Manual Issue December 2015.pdf'} at \textbf{`waggle/docs/alphasense-opc-n2'}.

\paragraph{$\bullet$ Histogram}
Histogram of alpha sensor is 62 bytes of reading. This parameter provides various information as listed below. \textbf{All data from the alpha sensor is LSB first}.

\begin{table}[h!]
    \centering
    \caption{Sub-packet Alpha sensor histogram}
    \begin{tabular}{|c|c|c|}
        \hline
        \rowcolor{black!8}
        \textbf{0x28} & \textbf{0xBE} & \textbf{Various sensor information as listed above}\\
        \hline
        Byte[0] & Byte[1] & Bytes[2 -- 63] \\ \hline
    \end{tabular}
\end{table}


\begin{itemize}
\setlength\itemsep{0em}
\item[$\circ$] Bin Counts (Bin0 - Bin15) are unsinged 16 bit integer variables (Bytes[2 -- 33]).
\item[$\circ$] An unsigned 8-bit integer represents the average amount of time that particles sized in the stated bin took cross the laser beam of the sensor. Value 10 represents 3.33 $\mu$s (Bytes[34 -- 37]).
\item[$\circ$] The sample flow rate in ml/s is provided as a float variable (Bytes[38 -- 41]).
\item[$\circ$] Temperature and Pressure alternating. Temperature is an unsigned 32-bit integer that represents temperature in Celsious multiplied by 10. Pressure is an unsigned 32-bit integer that represents pressure in pascals (Bytes[42 -- 45]).
\item[$\circ$] Actual sampling period of a measure of the historgam in seconds provided as 4 bytes of float variables (Bytes[46 -- 49]).
\item[$\circ$] The least significat 16-bit of the sum of the counts in all the histogram bins is provided by unsigned 16bit integers (Bytes[50 -- 51]).
\item[$\circ$] A float variable occupying 4 bytes for PM1. Unit is $\mu$g/m$^3$ (Bytes[52 -- 55]).
\item[$\circ$] A float variable occupying 4 bytes for PM2.5. Unit is $\mu$g/m$^3$ (Bytes[56 -- 59]).
\item[$\circ$] A float variable occupying 4 bytes for PM10. Unit is $\mu$g/m$^3$ (Bytes[60 -- 63]).
\end{itemize}


\begin{table}[h!]
    \centering
    \caption{Detail sub-packet of Alpha sensor histogram}
    \begin{tabular}{|>{\centering\arraybackslash}p{0.3\textwidth}|>{\centering\arraybackslash}p{0.2\textwidth}|}
        \hline
        \rowcolor{black!8}
        \textbf{Parameter} & \textbf{Data location}\\ \hline
        Bin Count (32 Bytes) & Bytes[2 - 33] \\ \hline
        Average Time (4 Bytes) & Bytes[34 -- 37] \\ \hline
        Sample flow rate (4 Bytes) & Bytes[38 -- 41] \\ \hline
        Temp/Pressure(alter) (4 Bytes) & Bytes[42 -- 45] \\ \hline
        Sampling period (4 Bytes) & Bytes[46 -- 49] \\ \hline
        Sum of the counts (2 Bytes) & Bytes[50 -- 51] \\ \hline
        PM1 (4 Bytes) & Bytes[51 -- 55] \\ \hline
        PM2.5 (4 Bytes) & Bytes[56 -- 59] \\ \hline
        PM10 (4 Bytes) & Bytes[60 -- 63] \\ \hline
    \end{tabular}
\end{table}



\paragraph{$\bullet$ Serial}
Serial of alpha sensor is 20 bytes of reading. This parameter provides the serial number of the alpha sensor by character.\\


\begin{table}[h!]
    \centering
    \caption{Sub-packet of Alpha sensor serial number}
    \begin{tabular}{|c|c|c|}
        \hline
        \rowcolor{black!8}
        \textbf{0x29} & \textbf{0x94} & \textbf{Raw values}\\
        \hline
        Byte[0] & Byte[1] & Bytes[2 -- 21] \\ \hline
    \end{tabular}
\end{table}


\paragraph{$\bullet$ Firmware}
Firmware of alpha sensor is 2 bytes of reading. This parameter provides the Firmware version of the alpha sensor by two unsigned 8-bit integer.\\


\begin{table}[h!]
    \centering
    \caption{Sub-packet of Alpha sensor firmware}
    \begin{tabular}{|c|c|c|}
        \hline
        \rowcolor{black!8}
        \textbf{0x30} & \textbf{0x82} & \textbf{Raw values}\\
        \hline
        Byte[0] & Byte[1] & Bytes[2 -- 3] \\ \hline
    \end{tabular}
\end{table}

\paragraph{$\bullet$ Status}
Status of alpha sensor is 4 bytes of reading. This parameter provides status of the alpha sensor in terms of if fan and laser are on/off and DAC value of the fan and laser.\\

\begin{table}[h!]
    \centering
    \caption{Sub-packet of Alpha sensor firmware}
    \begin{tabular}{|c|c|c|}
        \hline
        \rowcolor{black!8}
        \textbf{0x2B} & \textbf{0x84} & \textbf{Raw values}\\
        \hline
        Byte[0] & Byte[1] & Bytes[2 -- 5] \\ \hline
    \end{tabular}
\end{table}


\begin{table}[h!]
    \centering
    \caption{Detail sub-packet of Alpha sensor histogram}
    \begin{tabular}{|>{\centering\arraybackslash}p{0.3\textwidth}|>{\centering\arraybackslash}p{0.2\textwidth}|}
        \hline
        \rowcolor{black!8}
        \textbf{Parameter} & \textbf{Data location}\\ \hline
        Fan on/off (1 Byte, 0 or 1) & Bytes[2] \\ \hline
        Laser on/off (1 Byte, 0 or 1) & Bytes[3] \\ \hline
        Fan DAC value (1 Byte) & Bytes[4] \\ \hline
        Laser DAC value (1 Byte) & Bytes[5] \\ \hline
    \end{tabular}
\end{table}


\paragraph{$\bullet$ Configuration}
\textbf{THIS DATA DO NOT FOLLOW CORESENSE PACKET FORMAT, NO FORMAT AT ALL}
Configuration of alpha sensor is 256 bytes of reading. 
This parameter provides various information as listed below.
Since this configuration data is too long to fit into a sub-packet, the data are not packed into coresense packet.


\newcolumntype{a}{>{\columncolor{black!8}}c}
\begin{table}[h!]
    \centering
    \caption{Sub-packet of alpha sensor configuration}
    \begin{tabular}{|a|c|}
        \hline
        \textbf{1st line} & ``Start sending alpha sensor configuration'' \\ \hline
        \textbf{2nd line} & 256 bytes of raw reading (Binary) \\ \hline
        \textbf{last line} & ``End sending alpha sensor configuration'' \\ \hline
    \end{tabular}
\end{table}


\begin{itemize}
\setlength\itemsep{0em}
\item[$\circ$] Bin Boundaries (BB0 - BB14) are unsinged 16 bit integer variables, and two spare bytes.
\item[$\circ$] Bin Particle Volumes (BPV0 - BPV15) are float variables occupyting 4 bytes each.
\item[$\circ$] Bin Particle Densities (BPD0 -- BPD15) are float variables occupying 4 bytes each.
\item[$\circ$] Bin Sample Volume Weightings (BSVW0 -- BSVW15) are float variables occupying 4 bytes each.
\item[$\circ$] Gain Scaling Coefficient (GSC) is float variable occupying 4 bytes.
\item[$\circ$] Sample flow rate is a float variable occupying 4 bytes.
\item[$\circ$] Laser DAC value is unsigned 8bit interger variable.
\item[$\circ$] Fan DAC value is unsigned 8bit integer variable.
\item[$\circ$] Time of Flight to Sample Flow Rate conversion factor is unsigned 8bit integer variable.
\item[$\circ$] 21 spare bytes follow Configuration variables.
\end{itemize}


\makeatletter
\setlength{\@fptop}{0pt}
\makeatother

\begin{table}[h!]
    \centering
    \caption{Detail second lind of Alpha sensor configuration}
    \begin{tabular}{|>{\centering\arraybackslash}p{0.5\textwidth}|>{\centering\arraybackslash}p{0.2\textwidth}|}
    % \begin{tabular}{|c|c|}
        \hline
        \rowcolor{black!8}
        \textbf{Parameter} & \textbf{Data location}\\ \hline
        Bin Boundaries (32 Bytes) & Bytes[0 -- 31] \\ \hline
        Bin Particle Volumes (64 Bytes) & Bytes[32 -- 95] \\ \hline
        Bin Particle Densities (64 Bytes) & Bytes[96 -- 159] \\ \hline
        Bin Sample Volume Weightings (64 Bytes) & Bytes[160 -- 223] \\ \hline
        Gain Scaling Coefficient (4 Bytes) & Bytes[224 -- 227] \\ \hline
        Sample Flow Rate (4 Bytes) & Bytes[228 -- 231] \\ \hline
        Laser DAC (1 Byte) & Byte[232] \\ \hline
        Fan DAC (1 Byte) & Byte[233] \\ \hline
        Conversion factor (1 Byte) & Byte[244] \\ \hline
        Spare Bytes (21 Bytes) & Bytes[245 -- 255] \\ \hline
    \end{tabular}
\end{table}

\clearpage